The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-04-01 exp-resurgence.tex
Set end zone thresholds to integer values
Also, update Airy contour picture.

\includegraphics[width=6.5cm]{figures/rays.png}

@@

With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du, \]
where $\mathcal{C}^\theta_1$ is the contour that passes through the point $u = \tfrac{1}{2}$ and projects to the ray $\mathcal{J}^\theta_{\zeta, 1}$ under the mapping $-\zeta = 4u^3 - 3u$.
\begin{center}
\includegraphics[width=10cm]{figures/thimble_Airy.png}
\captionof{figure}{These pictures of the $u$ and $\zeta$ planes show the contour $\mathcal{C}^{\pi/8}_1$ and its projection $\mathcal{J}^{\pi/8}_{\zeta, 1}$. \textcolor{orange}{[Add $\zeta$ plane picture.]} The light and dark checks are the preimages of the upper and lower halves of the $\zeta$ plane, respectively. The region $\Re(\zeta) > 4$ is shaded and its preimage in the $u$ plane are shaded.}\label{fig:path_Airy}
\end{center}

>>>>

\includegraphics[width=6.5cm]{figures/rays_ge6.png}

@@

With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du, \]
where $\mathcal{C}^\theta_1$ is the contour that passes through the point $u = \tfrac{1}{2}$ and projects to the ray $\mathcal{J}^\theta_{\zeta, 1}$ under the mapping $-\zeta = 4u^3 - 3u$.
\begin{center}
\includegraphics[width=6.5cm]{figures/ray_1_ge3.png}
\hspace{0.5cm}
\includegraphics[width=6.5cm]{figures/thimble-n3_1.png}
\captionof{figure}{The ray $\mathcal{J}^{\pi/8}_{\zeta, 1}$ in the $\zeta$ plane and its preimage $\mathcal{C}^{\pi/8}_1$ in the $u$ plane. The upper and lower halves of the $\zeta$ plane are colored light and dark, so their preimages form a checker pattern on the $u$ plane. The region $\Re(\zeta) > 3$ and its preimage in the $u$ plane are shaded.}\label{fig:path_Airy}
\end{center}
